---
output: 
  pdf_document:
      number_section: yes
header-includes:
- \usepackage{fancyhdr}
- \usepackage{graphicx}
- \pagestyle{fancy}
- \setlength{\headheight}{30pt}
- \fancyfoot[L]{}
- \fancyhead[L]{\includegraphics[height=10mm,width=38mm]{UCLouvain - ecole-statistique.jpg}}
- \fancyhead[R]{}
- \fancyfoot[C]{\thepage}
- \fancyfoot[R]{\textit{Mathias Dah Fienon}}
- \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, comment = "", include = TRUE, warning = FALSE, message = FALSE)
```

\thispagestyle{empty}
\pagenumbering{gobble}
\includegraphics[width=3in, height=0.65in]{UCLouvain - ecole-statistique.jpg}
\hfill
\includegraphics[width=2in, height=0.6in]{logo_fac_scien.png} 
\vspace{1.5cm}
\newline
\vspace{1cm}
\begin{center}
    \hrulefill
    \vspace{1.2cm}
    \centerline{\textbf{\Large LSTAT2150}}
    \vspace{0.5cm}
    \newline
    \textbf{\Large NON PARAMETRIC CURVE ESTIMATION: }
    \vspace{0.2cm}
    \textbf{\Large SMOOTHING METHODS }
\end{center}
\vspace{0.8cm}
\hrulefill
\vspace{1.2cm}
\begin{center}
    \centerline{\textbf{\Large Project 34 :}}
    \vspace{0.5cm}
    \textbf{\Large \textit{Confdence intervals for non-parametric regression}} 
\end{center}
\vspace{1.2cm}
\begin{center}
    \textbf{\Large Project report} 
\end{center}
\vspace{1.2cm}
\begin{center}
    \textbf{\large Author : } 
\end{center}
\vspace{0.1cm}
\begin{center}
    \textbf{ \Large Mathias Dah Fienon, } \textit{\large noma :04452100 }
\end{center}
\vspace{4cm}
\begin{center}
    \textbf{\Large Academic year: } \textit{\large 2022-2023}
\end{center}

\newpage

\centerline{\huge \textit{Confdence intervals for non-parametric regression}}
\tableofcontents


\newpage
\pagenumbering{arabic}

```{r, child="project.Rmd"}
```

